### 2016-07-29 text/abstraction_relation.tex
Updates to building PCs.
Replace DSLTrans section with Frankenstein from different sources.

\subsection{Path Conditions}
\label{sec:gen_path_conds}

@@

\begin{figure}[htb]
        \centering
        \begin{subfigure}[b]{0.24\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/building_path_conditions/traceability_links.pdf}
                \caption{Before symbolic traceability links added}
                \label{fig:traceability_links1}
        \end{subfigure}%
        ~~
        \begin{subfigure}[b]{0.235\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/building_path_conditions/traceability_links2.pdf}
                \caption{After symbolic traceability links added}
                \label{fig:traceability_links2}
        \end{subfigure}%
        \caption{Symbolic traceability links created for an abstract DSLTrans rule}
        \label{fig:trace_links}
\end{figure}

@@

\begin{figure}[htb]
        \centering
        \begin{subfigure}[b]{0.235\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/building_path_conditions/backward_link.pdf}
                \caption{Rule with backward links (dashed lines)}
                \label{fig:backward_links}
        \end{subfigure}%
        ~~
        \begin{subfigure}[b]{0.235\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/building_path_conditions/backward_link2.pdf}
                \caption{Traceability links added\\~}
                \label{fig:backward_links2}
        \end{subfigure}%
        \caption{Adding traceability links to an abstract DSLTrans rule with backward links}
        \label{fig:back_links}
\end{figure}

@@

\begin{figure}[htb]
        \centering
        \begin{subfigure}[b]{0.40\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/empty_pc.pdf}
               	\caption{Abstraction holds}
               	\label{fig:empty_pc_success}
        \end{subfigure}%
        ~~\\
        \begin{subfigure}[b]{0.40\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/empty_pc2.pdf}
                \caption{Abstraction does not hold}
                \label{fig:empty_pc_fail}
        \end{subfigure}%
        \caption{Abstraction of transformation executions by the empty path condition}
        \label{fig:empty_pc}
\end{figure}

@@

\begin{figure}[htb]
        \centering
        \begin{subfigure}[b]{0.40\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/non_overlapping.pdf}
               	\caption{Abstraction holds on match and apply graphs}
               	\label{fig:non_overlapping_match_apply}
        \end{subfigure}%
        ~~\\
        \begin{subfigure}[b]{0.40\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/non_overlapping_trace_links.pdf}
                \caption{Abstraction holds on traceability links}
                \label{fig:non_overlapping_trace_links}
        \end{subfigure}%
        \caption{Abstraction of transformation execution by non-overlapping rule components}
        \label{fig:non_overlapping}
\end{figure}

\begin{figure}[htb]
        \centering
        \begin{subfigure}[b]{0.40\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/non_overlapping2.pdf}
               	\caption{Abstraction holds on match and apply graphs}
               	\label{fig:non_overlapping2_match_apply}
        \end{subfigure}%
        ~~\\
        \begin{subfigure}[b]{0.40\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/non_overlapping2_trace_links.pdf}
                \caption{Abstraction holds on traceability links}
                \label{fig:non_overlapping2_trace_links}
        \end{subfigure}%
        \caption{Example of abstraction over multiple rule execution}
        \label{fig:non_overlapping2}
\end{figure}

@@

\begin{figure}[htb]
        \centering
        \begin{subfigure}[b]{0.40\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/overlapping.pdf}
               	\caption{Abstraction holds on match and apply graphs}
               	\label{fig:overlapping_match_apply}
        \end{subfigure}%
        ~~\\
        \begin{subfigure}[b]{0.40\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/overlapping_trace_links.pdf}
                \caption{Abstraction holds on traceability links}
                \label{fig:overlapping_trace_links}
        \end{subfigure}%
        \caption{Abstraction of transformation execution by overlapping rule components}
        \label{fig:overlapping}
\end{figure}

@@

\begin{figure}[htb]
        \centering
        \begin{subfigure}[b]{0.40\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/overlapping2.pdf}
               	\caption{Elements cannot overlap within a component}
               	\label{fig:overlapping2_match_apply}
        \end{subfigure}%
        ~~\\
        \begin{subfigure}[b]{0.40\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/overlapping2_trace_links.pdf}
                \caption{Traceability links cannot be found}
                \label{fig:overlapping2_trace_links}
        \end{subfigure}%
        \caption{Abstraction does not hold}
        \label{fig:overlapping2}
\end{figure}

@@

\begin{figure}[htb]
        \centering
        \begin{subfigure}[b]{0.40\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/indirect.pdf}
               	\caption{Matching over match and apply graphs}
               	\label{fig:indirect_match_apply}
        \end{subfigure}%
        ~~\\
        \begin{subfigure}[b]{0.40\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/indirect_trace_links.pdf}
                \caption{Matching over traceability links}
                \label{fig:indirect_trace_links}
        \end{subfigure}%
        \caption{Abstraction with indirect links}
        \label{fig:indirect}
\end{figure}

\begin{figure*}[htb]
        \centering
        \begin{subfigure}[b]{0.70\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/combination.pdf}
               	\caption{Abstraction holds on match and apply graphs}
               	\label{fig:combination_match_apply}
        \end{subfigure}%
        ~~\\
        \begin{subfigure}[b]{0.70\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/combination_trace_links.pdf}
                \caption{Abstraction holds on traceability links}
                \label{fig:combination_trace_links}
        \end{subfigure}%
        \caption{Abstraction where path condition has combined rules}
        \label{fig:combination}
\end{figure*}

>>>>

\subsection{Path Conditions}
\label{subsec:gen_path_conds}

@@

%\begin{figure}[htb]
%        \centering
%        \begin{subfigure}[b]{0.24\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/building_path_conditions/traceability_links.pdf}
%                \caption{Before symbolic traceability links added}
%                \label{fig:traceability_links1}
%        \end{subfigure}%
%        ~~
%        \begin{subfigure}[b]{0.235\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/building_path_conditions/traceability_links2.pdf}
%                \caption{After symbolic traceability links added}
%                \label{fig:traceability_links2}
%        \end{subfigure}%
%        \caption{Symbolic traceability links created for an abstract DSLTrans rule}
%        \label{fig:trace_links}
%\end{figure}

@@

%\begin{figure}[htb]
%        \centering
%        \begin{subfigure}[b]{0.235\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/building_path_conditions/backward_link.pdf}
%                \caption{Rule with backward links (dashed lines)}
%                \label{fig:backward_links}
%        \end{subfigure}%
%        ~~
%        \begin{subfigure}[b]{0.235\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/building_path_conditions/backward_link2.pdf}
%                \caption{Traceability links added\\~}
%                \label{fig:backward_links2}
%        \end{subfigure}%
%        \caption{Adding traceability links to an abstract DSLTrans rule with backward links}
%        \label{fig:back_links}
%\end{figure}

@@

%\begin{figure}[htb]
%        \centering
%        \begin{subfigure}[b]{0.40\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/empty_pc.pdf}
%               	\caption{Abstraction holds}
%               	\label{fig:empty_pc_success}
%        \end{subfigure}%
%        ~~\\
%        \begin{subfigure}[b]{0.40\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/empty_pc2.pdf}
%                \caption{Abstraction does not hold}
%                \label{fig:empty_pc_fail}
%        \end{subfigure}%
%        \caption{Abstraction of transformation executions by the empty path condition}
%        \label{fig:empty_pc}
%\end{figure}

@@

%\begin{figure}[htb]
%        \centering
%        \begin{subfigure}[b]{0.40\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/non_overlapping.pdf}
%               	\caption{Abstraction holds on match and apply graphs}
%               	\label{fig:non_overlapping_match_apply}
%        \end{subfigure}%
%        ~~\\
%        \begin{subfigure}[b]{0.40\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/non_overlapping_trace_links.pdf}
%                \caption{Abstraction holds on traceability links}
%                \label{fig:non_overlapping_trace_links}
%        \end{subfigure}%
%        \caption{Abstraction of transformation execution by non-overlapping rule components}
%        \label{fig:non_overlapping}
%\end{figure}
%
%
%\begin{figure}[htb]
%        \centering
%        \begin{subfigure}[b]{0.40\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/non_overlapping2.pdf}
%               	\caption{Abstraction holds on match and apply graphs}
%               	\label{fig:non_overlapping2_match_apply}
%        \end{subfigure}%
%        ~~\\
%        \begin{subfigure}[b]{0.40\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/non_overlapping2_trace_links.pdf}
%                \caption{Abstraction holds on traceability links}
%                \label{fig:non_overlapping2_trace_links}
%        \end{subfigure}%
%        \caption{Example of abstraction over multiple rule execution}
%        \label{fig:non_overlapping2}
%\end{figure}

@@

%\begin{figure}[htb]
%        \centering
%        \begin{subfigure}[b]{0.40\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/overlapping.pdf}
%               	\caption{Abstraction holds on match and apply graphs}
%               	\label{fig:overlapping_match_apply}
%        \end{subfigure}%
%        ~~\\
%        \begin{subfigure}[b]{0.40\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/overlapping_trace_links.pdf}
%                \caption{Abstraction holds on traceability links}
%                \label{fig:overlapping_trace_links}
%        \end{subfigure}%
%        \caption{Abstraction of transformation execution by overlapping rule components}
%        \label{fig:overlapping}
%\end{figure}

@@

%\begin{figure}[htb]
%        \centering
%        \begin{subfigure}[b]{0.40\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/overlapping2.pdf}
%               	\caption{Elements cannot overlap within a component}
%               	\label{fig:overlapping2_match_apply}
%        \end{subfigure}%
%        ~~\\
%        \begin{subfigure}[b]{0.40\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/overlapping2_trace_links.pdf}
%                \caption{Traceability links cannot be found}
%                \label{fig:overlapping2_trace_links}
%        \end{subfigure}%
%        \caption{Abstraction does not hold}
%        \label{fig:overlapping2}
%\end{figure}

@@

%\begin{figure}[htb]
%        \centering
%        \begin{subfigure}[b]{0.40\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/indirect.pdf}
%               	\caption{Matching over match and apply graphs}
%               	\label{fig:indirect_match_apply}
%        \end{subfigure}%
%        ~~\\
%        \begin{subfigure}[b]{0.40\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/indirect_trace_links.pdf}
%                \caption{Matching over traceability links}
%                \label{fig:indirect_trace_links}
%        \end{subfigure}%
%        \caption{Abstraction with indirect links}
%        \label{fig:indirect}
%\end{figure}
%
%\begin{figure*}[htb]
%        \centering
%        \begin{subfigure}[b]{0.70\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/combination.pdf}
%               	\caption{Abstraction holds on match and apply graphs}
%               	\label{fig:combination_match_apply}
%        \end{subfigure}%
%        ~~\\
%        \begin{subfigure}[b]{0.70\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/abstraction_relation/combination_trace_links.pdf}
%                \caption{Abstraction holds on traceability links}
%                \label{fig:combination_trace_links}
%        \end{subfigure}%
%        \caption{Abstraction where path condition has combined rules}
%        \label{fig:combination}
%\end{figure*}

### 2016-07-29 text/building_path_conditions.tex
Replace DSLTrans section with Frankenstein from different sources.

\begin{figure*}[htb]
        \centering
        \begin{subfigure}[b]{0.34\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/building_path_conditions/next_layer.pdf}
                \caption{Previous path conditions are combined\\ with rules}
                \label{fig:next_layer}
        \end{subfigure}%
        ~~
        \begin{subfigure}[b]{0.34\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/overview/layers_pc.pdf}
                \caption{Combining a path condition with two rules\\~}
                \label{fig:layers_pc2}
        \end{subfigure}%

         \caption{Two components in the path condition creation process}
         \label{fig:combining_path_conditions}
\end{figure*}

@@

\begin{figure*}[htb]
        \centering
        \begin{subfigure}[b]{0.7\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/building_path_conditions/total_satisfied_dependencies.pdf}
                \caption{Totally satisfied at one location}
                \label{fig:total_satisfied_dependencies}
        \end{subfigure}%
        \\
        \begin{subfigure}[b]{0.8\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/building_path_conditions/multiple_total_satisfied_dependencies.pdf}
                \caption{Totally satisfied at multiple locations - \reviewer{Fix boxes on bottom}}
                \label{fig:multiple_total_satisfied_dependencies}
        \end{subfigure}%
        \caption{R's dependencies are totally satisfied by PC}
        \label{fig:totes_sat_deps}
\end{figure*}

>>>>

%\begin{figure*}[htb]
%        \centering
%        \begin{subfigure}[b]{0.34\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/building_path_conditions/next_layer.pdf}
%                \caption{Previous path conditions are combined\\ with rules}
%                \label{fig:next_layer}
%        \end{subfigure}%
%        ~~
%        \begin{subfigure}[b]{0.34\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/overview/layers_pc.pdf}
%                \caption{Combining a path condition with two rules\\~}
%                \label{fig:layers_pc2}
%        \end{subfigure}%
%        
%       
%         \caption{Two components in the path condition creation process}
%         \label{fig:combining_path_conditions}
%\end{figure*}

@@

%\begin{figure*}[htb]
%        \centering
%        \begin{subfigure}[b]{0.7\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/building_path_conditions/total_satisfied_dependencies.pdf}
%                \caption{Totally satisfied at one location}
%                \label{fig:total_satisfied_dependencies}
%        \end{subfigure}%
%        \\
%        \begin{subfigure}[b]{0.8\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/building_path_conditions/multiple_total_satisfied_dependencies.pdf}
%                \caption{Totally satisfied at multiple locations - \reviewer{Fix boxes on bottom}}
%                \label{fig:multiple_total_satisfied_dependencies}
%        \end{subfigure}%
%        \caption{R's dependencies are totally satisfied by PC}
%        \label{fig:totes_sat_deps}
%\end{figure*}
